Do we need detailed demographic data to forecast plant population responses to climate change?

### 2014-12-12 manuscript/manuscript.Rmd
new readme for subdirectories
just trying to get refs to work

Recently, Freckelton et al., building on work by Hastings and NAME, have proposed density-structured population models that focus on the transition of populations among discrete states, rather than the traditional approach of modeling the transitions of individuals. Such an approach could be extremely valuable because the data needed to parameterize density-structured population models is much easier, and less costly, to collect (Queenborough et al. year). For example, using a density-structured approach, one could build a population model using a time series of annual plot-based censuses of species percent cover. However, a major assumption of the density-structured approach is that the aggregate dynamics of the population observed at coarse spatial resolution faithfully represent, and correspond to, the fates of individual plants. In other words, using a density-structured approach requires a leap of faith that important covariates (e.g., climate variables) at the level of the individual are captured adequately at the population level. If we seek to forecast the impacts of climate change on plant populations, then clearly this assumption requires testing.

@@

```{r figure_3, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated ``` r nSims``` times. Note that the y-axes vary across panels. The light blue line shows the difference between the observed-year percent cover and the average cover observed across all years. The models tend to underpredict and perform poorly when observed cover in a given year is a large deviant from the mean.", fig.width=5, fig.height=6, cache=FALSE, results='hide'}
library(plyr)
library(reshape2)
resD <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_Residuals.rds")
nSims <- length(unique(resD$sim))
diffD <- ddply(resD, c("year", "species"), summarise,
               avgDiff = mean(yearDiff))

@@

>>>>

Recently, @Freckleton2011, building on work by Hastings and NAME, have proposed density-structured population models that focus on the transition of populations among discrete states, rather than the traditional approach of modeling the transitions of individuals. Such an approach could be extremely valuable because the data needed to parameterize density-structured population models is much easier, and less costly, to collect (Queenborough et al. year). For example, using a density-structured approach, one could build a population model using a time series of annual plot-based censuses of species percent cover. However, a major assumption of the density-structured approach is that the aggregate dynamics of the population observed at coarse spatial resolution faithfully represent, and correspond to, the fates of individual plants. In other words, using a density-structured approach requires a leap of faith that important covariates (e.g., climate variables) at the level of the individual are captured adequately at the population level. If we seek to forecast the impacts of climate change on plant populations, then clearly this assumption requires testing.

@@

```{r figure_3, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated `r nSims` times. Note that the y-axes vary across panels. The light blue line shows the difference between the observed-year percent cover and the average cover observed across all years. The models tend to underpredict and perform poorly when observed cover in a given year is a large deviant from the mean.", fig.width=5, fig.height=6, cache=FALSE, results='hide'}
library(plyr)
library(reshape2)
resD <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_Residuals.rds")
nSims <- length(unique(resD$sim))
diffD <- ddply(resD, c("year", "species"), summarise,
               avgDiff = mean(yearDiff))

@@

References
==========
